SST_patterns

### 2020-04-06 SST_patterns.Rmd
UPDATE
update

distance_corr <- combined_freq_spread %>% 
  group_by(site, product) %>% 
  slope_calc()
```

@@

## Comparing the relationship between 10 km and 30km from coastline and 10km and 50km from the coastline

combined <- rbind(CMC_count,G1SST_count,MUR_count,OISST_count)
```

>>>>

@@

## Using series of general linear hypotheses (Hothorn et al., 2008) to look for differences in upwelling signal metrics between datasets and between sites
# Is there a significant difference in the count between the datasets at a particular site

```{r}
load("Data/OISST_upwell_base.RData")
load("Data/CMC_upwell_base.RData")
load("Data/SACTN_upwell_base.RData")
load("Data/MUR_upwell_base.RData")
load("Data/G1SST_upwell_base.RData")
```
